Basic Model formulation

### 2015-04-14 documentation/model_formulation.Rmd
add lattice

>>>>

```{r, eval = FALSE, dev='png', echo = FALSE, fig.show='animate', fig.height = 4, fig.width = 4, interval = 0.01}
if(Sys.info()[['sysname']] == "Linux") X11.options(antialias = "none") #for Linux Systems to enable pixel-wise plotting in (animated) gif-files. 
  if(Sys.info()[['sysname']] == "Windows") windows.options(antialias = "none") #for Windows Systems to enable pixel-wise plotting in (animated) gif-files. 
  width = nullmodel$timeseries[[1]]$dim[1]
  height = nullmodel$timeseries[[1]]$dim[2]

    for(i in 1:length(nullmodel$timeseries) ) {
      par(mar = c(0,0,0,0))
      plot(nullmodel$timeseries[[i]], grid = FALSE, ani = TRUE) 
    }
```
